Analysis for Non-Expressive performances (OFFSET)

### 2020-04-14 material/analysis/stim_n/ioi_offset.Rmd
update offset analysis
Signed-off-by: Atsuko Tominaga <Tominaga_Atsuko@phd.ceu.edu>

```{r extract, include = FALSE}
df_ioi <- fread("./preprocessor/filtered/data_offset.csv", header = T, sep = ",", dec = ".") # read a filtered csv

# SubNr as a factor
df_ioi$SubNr <- as.factor(df_ioi$SubNr)

# assign RowNr
df_ioi$RowNr <- rep(1:72, nrow(df_ioi)/72)
```

```{r normIOIs, include = FALSE}
# calculate normIOIs
df_ioi$IOI <- diff(c(0, df_ioi$TimeStamp))

# convert bpm to ms
df_ioi[Tempo == 120]$Tempo <- 250
df_ioi[Tempo == 110]$Tempo <- 273
df_ioi[Tempo == 100]$Tempo <- 300

# normalise IOIs
df_ioi$normIOI <- df_ioi$IOI/df_ioi$Tempo

# remove the first note
df_ioi <- df_ioi[RowNr != 1]

# assign Interval
df_ioi$Interval <- rep(1:71, nrow(df_ioi)/71)

# remove irrelevant intervals
ls_irrelevant <- list(c(25:28), c(32:35), c(51:52), c(56:57), c(65:71))
df_ioi$EighthNote <- "Yes"

for (phrase in 1:length(ls_irrelevant)){
  for (note in 1:length(ls_irrelevant[[phrase]])){
    df_ioi[Interval == ls_irrelevant[[phrase]][note]]$EighthNote <- "No"
  }
}
```

@@

@@

```{r ioi_all, echo = FALSE}
# Group mean
ioi_all <- df_ioi[EighthNote == "Yes", .(N = length(normIOI), Mean = mean(normIOI), SD = sd(normIOI))]
print(ioi_all)
```

## Sequence plot
```{r seq, fig.width = 10, echo = FALSE}
# For each individual
ioi_seq <- df_ioi[EighthNote == "Yes", .(N = length(normIOI), Mean = mean(normIOI), SD = sd(normIOI)), .(SubNr, Interval)]

p_ioi_seq <- ggplot(data = ioi_seq, aes(x = Interval, y = Mean, colour = SubNr)) +
  geom_line() +
  geom_point() +
  geom_hline(yintercept = 1, linetype = "dashed") + # Tempo
  geom_errorbar(aes(ymin = Mean - SD, ymax = Mean + SD), width=.2,
                position = position_dodge(.05)) + 
  labs(x = "Interval", y = "Normalised IOI") + scale_x_continuous(breaks=seq(1,66,1))
p_ioi_seq
```

## Exclude outlier participants
```{r outlier, echo = FALSE}
excluded_ioi <- ioi[Mean < mean(ioi$Mean)+3*mean(ioi$SD) & Mean > mean(ioi$Mean)-3*mean(ioi$SD)]
print(excluded_ioi)
```

```{r export, include = FALSE}
# export df_ioi
write.csv(df_ioi, file = "./data_ioi_offset.csv", row.names = F)
```

>>>>

```{r extract, include = FALSE}
dt_ioi <- fread("./preprocessor/filtered/data_offset.csv", header = T, sep = ",", dec = ".") # read a filtered csv

# SubNr as a factor
dt_ioi$SubNr <- as.factor(dt_ioi$SubNr)

# assign RowNr
dt_ioi$RowNr <- rep(1:72, nrow(dt_ioi)/72)
```

```{r normIOIs, include = FALSE}
# calculate normIOIs
dt_ioi$IOI <- diff(c(0, dt_ioi$TimeStamp))

# convert bpm to ms
dt_ioi[Tempo == 120]$Tempo <- 250
dt_ioi[Tempo == 110]$Tempo <- 273
dt_ioi[Tempo == 100]$Tempo <- 300

# normalise IOIs
dt_ioi$normIOI <- dt_ioi$IOI/dt_ioi$Tempo

# remove the first note
dt_ioi <- dt_ioi[RowNr != 1]

# assign Interval
dt_ioi$Interval <- rep(1:71, nrow(dt_ioi)/71)

# remove irrelevant intervals
ls_irrelevant <- list(c(25:28), c(32:35), c(51:52), c(56:57), c(65:71))
dt_ioi$EighthNote <- "Yes"

for (phrase in 1:length(ls_irrelevant)){
  for (note in 1:length(ls_irrelevant[[phrase]])){
    dt_ioi[Interval == ls_irrelevant[[phrase]][note]]$EighthNote <- "No"
  }
}
```

@@

#### Sequence plot
- Right wrap: Subject Number
- A dashed line represents the ideal tempo

```{r ioi_seq, fig.width = 14, fig.height = 12, echo = FALSE}
# For each individual
ioi_seq <- dt_ioi[EighthNote == "Yes", .(N = length(normIOI), Mean = mean(normIOI)), by = .(SubNr, TrialNr, Interval)]

p_ioi_seq <- ggplot(data = ioi_seq, aes(x = Interval, y = Mean, group = TrialNr)) +
  geom_line() +
  geom_point() +
  geom_hline(yintercept = 1, linetype = "dashed") + # Tempo
  facet_grid(SubNr ~ .) +
  labs(x = "Interval", y = "Normalised IOI") + scale_x_continuous(breaks=seq(1,66,1))
p_ioi_seq
```

#### Distribution plot
- Right wrap: Trial Number
- Upper wrap: Subject Number

```{r ioi_dis, fig.width = 14, fig.height = 8, echo = FALSE}
p_ioi_dis <- ggplot(dt_ioi[EighthNote == "Yes"], aes(x = normIOI)) +
  geom_histogram(binwidth = .02, alpha = .5, position = "identity") +
  facet_grid(TrialNr ~ SubNr) +
  labs(x = "Normalised IOI", y = "Count", subtitle = "IOI: Non-Expression")
p_ioi_dis
```

@@

```{r ioi_all, echo = FALSE}
# Group mean
ioi_all <- ioi[, .(N = length(Mean), Mean = mean(Mean), SD = sd(Mean))]
print(ioi_all)
```

### Exclude outlier participants
```{r outlier, echo = FALSE}
excluded_ioi <- ioi[Mean < ioi_all$Mean+3*ioi_all$SD & Mean > ioi_all$Mean-3*ioi_all$SD]
print(excluded_ioi)
```

# IOI Variability
```{r cv, echo = FALSE}
# for each participant
cv <- dt_ioi[EighthNote == "Yes", .(N = length(normIOI), CV = sd(normIOI)/mean(normIOI)) , by = .(SubNr, TrialNr)]
cv
```

```{r cv_box, echo = FALSE}
p_cv_box <- ggplot(cv, aes(x = SubNr, y = CV)) +
  geom_boxplot() +
  geom_dotplot(binaxis = 'y', stackdir = 'center', dotsize = 0.5)
p_cv_box
```

### Exclude outlier performances
```{r cv_outlier, echo = FALSE}
# for all
cv_all <- cv[, .(N = length(CV), Mean = mean(CV), SD = sd(CV))]
print(cv_all)

excluded_cv <- cv[CV < cv_all$Mean+3*(cv_all$SD) & CV > cv_all$Mean-3*cv_all$SD]
print(excluded_cv)
```
